Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff-galois-slicing-via-grothendieck.tex
Sync summary of notes.
Diff* is (I think -- haven't checked) a full subcategory of Fam(FinVect^op).

\subsection{Galois slicing and automatic differentiation via Grothendieck construction}

\subsubsection{Galois slicing via category of families}

Now recall that $\Fam(\LatGal)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X, \LatGal)$, with:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}

\subsubsection{Automatic differentiation via categories of families}

@@

>>>>

\subsection{Galois slicing and automatic differentiation via Grothendieck construction}
\label{sec:galois-slicing-auto-diff-via-grothendieck}

\subsubsection{Galois slicing via a category of families}
\label{sec:galois-slicing-auto-diff-via-grothendieck:galois-slicing}

Recall that $\Fam(\LatGal)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X, \LatGal)$ which has:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}

The action of $\Fam(-,\LatGal)$ on a morphism $f: X \to Y$. Composition of any $(f, \partial f):$

\subsubsection{Automatic differentiation via categories of families}
\label{sec:galois-slicing-auto-diff-via-grothendieck:auto-diff}

@@

Similarly, $\Diff^*$ is equivalent to a full subcategory of $\Fam(\FinVect^\op)$ with composition
corresponding to the backward chain rule.
